---
title: "Clean Datasets (Small structures)"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE)

```

# Load libraries

```{r}
library(tidyverse)
library(skimr)
```

# Load data

```{r}
pBlanca<-read_csv(file = "./Datasets/BD_AranasPeq_Blanca.csv")
pCacique<-read_csv(file = "./Datasets/BD_AranasPeq_Cacique.csv")
```

# Check the data

Remove tags data and duplicated images

## Blanca (small structures)

```{r}
skim(pBlanca)

NAs<-which(is.na(pBlanca$photo.code))
pBlanca<-pBlanca[-NAs,]

NAs<-which(is.na(pBlanca$area.cm2))
pBlanca<-pBlanca[-NAs,]

# View(pBlanca[NAs,])
```

## Cacique (small structures)

```{r}
skim(pCacique)

# Image without photo code could be 3, I told Enrique to add the data
NAs<-which(is.na(pCacique$photo.code))
pCacique<-pCacique[-NAs,]

NAs<-which(is.na(pCacique$area.cm2))
pCacique<-pCacique[-NAs,]

# View(pCacique[NAs,])
```

The first 7 rows of Blanca's dataset were measured by side so I'll remove those records (actually 8, but 1 of those was removed due to being a tag)

```{r}
pBlanca<-pBlanca[-(1:7),]
```

# Format

Here, all three datasets will be formatted before combining them into one unique dataset.

```{r}
colnames(pBlanca)
colnames(pCacique)

columns<-c("photo.code", "str.code", "site", "month", 
           "year", "area.cm2", "num.frag", "mort.", "mort.parc", "perd",
           "blanq", "digitador")

filtered_pBlanca<-pBlanca %>% 
  select(all_of(columns))

filtered_pCacique<-pCacique %>% 
  select(all_of(columns))

final_ds_p<-rbind(filtered_pBlanca, filtered_pCacique)
```

# Fix the class/type of each variable

```{r}
final_ds2_p<-final_ds_p %>% 
  mutate(structure=as.factor(str.code),
         site=as.factor(site),
         data_entry_person=as.factor(digitador),
         month=as.factor(month),
         year=as.factor(year),
         .keep = "unused")

```

Now, we want to keep data from January 2020 to June 2024 

```{r}
final_ds2_p$date <- paste(final_ds2_p$year, final_ds2_p$month, sep = "-")
final_ds2_p$date <- ym(final_ds2_p$date)

final_ds2_p <- final_ds2_p %>% 
    filter(between(date, as_date("2021-01-01"), as_date("2024-06-01")))
```

Save the final dataset as a new csv.

```{r}
write.csv(final_ds2_p, 
          file = "./Datasets/small_spiders.csv",
          na = "NA",
          row.names = F)
```
