---
title: "Clean Datasets (Big structures)"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE)

```

# Load libraries

```{r}
library(tidyverse)
library(skimr)
``` 

# Load data

```{r}
Blanca<-read_csv(file = "./Datasets/BD_PBlanca_Monitoreo-amplio.csv")
Guiri<-read_csv(file = "./Datasets/BD_Guiri_Monitoreo_amplio.csv")
Pelonas<-read_csv(file = "./Datasets/BD_PPelonas_Monitoreo-amplio.csv")
```

# Check the data

Remove tags data and duplicated images

## Blanca

```{r}
skim(Blanca)

NAs<-which(is.na(Blanca$photo.code))
Blanca<-Blanca[-NAs,]

NAs<-which(is.na(Blanca$gira))
Blanca<-Blanca[-NAs,]

NAs<-which(is.na(Blanca$digitador))
Blanca<-Blanca[-NAs,]

NAs<-which(is.na(Blanca$lado))
Blanca<-Blanca[-NAs,]

NAs<-which(is.na(Blanca$area.cm2))
Blanca<-Blanca[-NAs,]

NAs<-which(is.na(Blanca$blanq))
Blanca<-Blanca[-NAs,]

# View(Blanca[NAs,])
```

## Guiri

```{r}
skim(Guiri)

NAs<-which(is.na(Guiri$photo.code))
Guiri<-Guiri[-NAs,]

NAs<-which(is.na(Guiri$area.cm2))
Guiri<-Guiri[-NAs,]

# View(Guiri[NAs,])
```

## Pelonas

```{r}
skim(Pelonas)

NAs<-which(is.na(Pelonas$photo.code))
Pelonas<-Pelonas[-NAs,]

NAs<-which(is.na(Pelonas$lado))
Pelonas<-Pelonas[-NAs,]

NAs<-which(is.na(Pelonas$area.cm2))
Pelonas<-Pelonas[-NAs,]

#View(Pelonas[NAs,])
```

# Format

Here, all three datasets will be formatted before combining them into one unique dataset.

```{r}
colnames(Pelonas)[19]<-"digitador"

columns<-c("photo.code", "str.code", "lado", "site", "origin", "month", 
           "year", "area.cm2", "num.frag", "mort.", "mort.parc", "perd",
           "blanq", "digitador")

filtered_blanca<-Blanca %>% 
  dplyr::select(all_of(columns))

filtered_guiri<-Guiri %>% 
  dplyr::select(all_of(columns))

filtered_pelonas<-Pelonas %>% 
  dplyr::select(all_of(columns))

final_ds<-rbind(filtered_blanca, filtered_guiri, filtered_pelonas)
```

Some structures tag have been replaced. However the structures remain the same. For that reason, it's necessary to re-assign the number to keep a continuity.

```{r}
source("./Scripts/fix_structure_code.R")
#final_ds$structure <- fix_structure(final_ds$structure)
final_ds$str_fixed <- fix_structure(final_ds$str.code)
```

# Origin

Each structure possesses coral fragments from specific origins. Those will be added to the datasets.

```{r}
source("./Scripts/asign_origin.R")

final_ds$origin<-asign_origin(final_ds$str_fixed)

NAs<-which(is.na(final_ds$origin))
final_ds[NAs,]
```


# Fix the class/type of each variable

```{r}
final_ds2<-final_ds %>% 
  mutate(structure=as.factor(str.code),
         structure_fixed=as.factor(str_fixed),
         site=as.factor(site),
         face=as.factor(lado),
         origin=as.factor(origin),
         data_entry_person=as.factor(digitador),
         month=as.factor(month),
         year=as.factor(year), 
         .keep = "unused")

```

Remove data analysed by Patricia, Andrea C. and Carmen. Patricia's data were recorded using wrong scales, whilst Andrea and Carmen's data are the same as Chiara's.

```{r}
levels(final_ds2$data_entry_person)

final_ds2 <- final_ds2 %>% 
  filter(!data_entry_person %in% c("Patricia", "Andrea C.", "Carmen")) %>% 
  droplevels()
```

Now, we want to keep data from January 2020 to June 2024 

```{r}
final_ds2$date <- paste(final_ds2$year, final_ds2$month, sep = "-")
final_ds2$date <- ym(final_ds2$date)

final_ds2 <- final_ds2 %>% 
    filter(between(date, as_date("2021-01-01"), as_date("2024-06-01")))
```

Varias fotografías están repetidas y con datos, por la misma persona.
Estos los removí del dataset pero aún se mantienen en la base de drive. Por ejemplo, ambas Andrea y Priscilla hicieron la estructura 97. Santiago y Chiara también tienen estructuras repetidas. Esta revisión la hice a mano por lo que no hay código. El código siguiente fue usado únicamente para identificar las observaciones.

```{r, eval=FALSE}
n_occur <- data.frame(table(final_ds2$photo.code, 
                            final_ds2$site,
                            final_ds2$month,
                            final_ds2$year))
n_occur[n_occur$Freq > 1,]
dups<-final_ds2[final_ds2$photo.code %in% n_occur$Var1[n_occur$Freq > 1],]
dups %>% arrange(photo.code) %>% View()
levels(as.factor(dups$photo.code))
```

Por último, es necesario censurar los nombres de los digitadores.

```{r}
levels(final_ds2$data_entry_person)<-paste("Digitador",
                                           as.character(seq(1,15,1)), 
                                           sep = "_")
```


Save the final dataset as a new csv.

```{r}
write.csv(final_ds2, 
          file = "./Datasets/big_spiders.csv",
          na = "NA",
          row.names = F)
```


