---
title: "CRGreport"
author: "R. Hidalgo"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

This report's objective is to provide a summary of the analyses done, in a way that is easy to read and understand.

Packages used:

```{r}
library(tidyverse)
library(lme4)
library(glmmTMB)
library(mgcv)
library(DHARMa)
library(sjPlot)
library(MASS)
library(skimr)
library(GGally)
library(DescTools)
library(ggeffects)
```

Data

```{r}
# setwd <- "C:/User0s/User/Desktop/Git/CRG_spider_nurseries" 

big <- read_csv("./Datasets/big_spiders.csv")
small <- read_csv("./Datasets/small_spiders.csv")
paleta <- c("#192639","#4EBCB8", "#FA9938", "#F4F4F5")

big <- big |>  
  mutate(structure=as.factor(structure),
         structure_fixed=as.factor(structure_fixed),
         site=as.factor(site),
         face=as.factor(face),
         origin=as.factor(origin),
         data_entry_person=as.factor(data_entry_person),
         month=as.factor(month),
         year=as.factor(year), 
         .keep = "unused")

small <- small %>% 
  mutate(structure=as.factor(structure),
         site=as.factor(site),
         data_entry_person=as.factor(data_entry_person),
         month=as.factor(month),
         year=as.factor(year),
         date=lubridate::as_date(small$date),
         .keep = "unused")
```


# Methods

There are two types of structures, big ones and small ones. Photographs of each of the sides of the spider structures were taken with a camera (model). In total, each structure has seven pictures each month, six faces and a top view. Small structures have only one photograph each. For each photograph, data on the live coral cover, number of fragments, number of dead fragments and number of bleached fragments were recorded. The total area (in cm2) of live coral for each of the seven sides of the spider structures was calculated using ImageJ (citation). 

Big structures: the area of live coral cover was analyzed using a generalized linear mixed model (GLMM) with a twiddle distribution. The model included site and date as fixed effects ad¿nd the structure itself as random effect. The model was fitted using the `glmmTMB` package (citation). Additionaly, due to high mortality towards the end of the period, date was included as a polynomial term to account for the non-linear trend. Some observations contained zero values due to such mortality, so a zero-inflated model was used to account for the excess of zeros in the data. Both fixes terms had a significant interaction. The number of dead fragments was also analyzed with a GLMM but with a negative binonial distribution to account for overdispersion. The model included site and date as fixed effects and the structure itself as random effect. Additionally, an offset was included to account for the number of fragments in each structure. Observations with zero values were not included in the model because the offset is log scaled.

# Analyses and Results (live coral)

## Model

```{r}
m5 <- glmmTMB(area.cm2 ~ poly(date, 2) * site + (1|structure_fixed),
                 data = df_1,
                 ziformula = ~ 1,
                 family = tweedie())

summary(m5)
DHARMa::simulateResiduals(fittedModel = m5, plot = TRUE)
```

## Estimates

```{r}
plot_model(m5, type = "est", transform = NULL)

# random effecrs, structure
ranef(m4)
plot_model(m4, type = "re", transform = NULL)
```

## Predictions

```{r}
# If that fails, generate predictions manually:
new_data <- expand.grid(site=levels(df_1$site),
                        date = seq(as.Date("2021-01-01"),
                                        as.Date("2024-05-01"),
                                        by = "month"),
                        structure_fixed=levels(df_1$structure_fixed))

# Include poly() terms manually
new_data$poly1 <- poly(df_1$date, 2)[,1][1:1148]
new_data$poly2 <- poly(df_1$date, 2)[,2][1:1148]

# Rename for consistency with model
names(new_data)[which(names(new_data) == "poly1")] <- "poly(date, 2)1"
names(new_data)[which(names(new_data) == "poly2")] <- "poly(date, 2)2"

new_data$preds <- predict(m5, newdata = new_data, type = "response")

# Plot with ggplot2
ggplot(new_data, aes(x = date, y = preds, col=site)) +
  stat_summary(geom = "line", fun = "mean", linewidth = 1) +
  labs(y = "Predicted area (cm²)", x = "Date")+
  scale_color_manual(values = paleta[c(2,3)],
                     labels = c("Güiri", "Playa Blanca"))+
  theme_classic()+
  theme(legend.position = "top",
        legend.title = element_blank()) 
```

# Dead fragments

## Model

```{r}
modelo_nb <- glmmTMB(
  mort. ~ date + site + offset(log(num.frag)) + (1 | structure_fixed),
  family = nbinom2,
  data = df_1_2
)
```

```{r}
summary(modelo_nb)
DHARMa::simulateResiduals(fittedModel = modelo_nb, plot = TRUE)
```
