---
title: "Plots"
author: "R. Hidalgo"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# General Plots 

```{r, echo=TRUE, eval=TRUE}
library(tidyverse)

#setwd("C:/Users/User/Desktop/Git/CRG_spider_nurseries")

big <- read_csv("./Datasets/big_spiders.csv")
small <- read_csv("./Datasets/small_spiders.csv")

paleta <- c("Playa Blanca" = "#192639", 
            "Playa Pelonas" = "#4EBCB8", 
            "Guiri" = "#FA9938", 
              "Cacique" = "#9E1B32")

big <- big |>  
  mutate(structure=as.factor(structure),
         structure_fixed=as.factor(structure_fixed),
         site=as.factor(site),
         face=as.factor(face),
         origin=as.factor(origin),
         data_entry_person=as.factor(data_entry_person),
         month=as.factor(month),
         year=as.factor(year),
         .keep = "unused")

small <- small %>% 
  mutate(structure=as.factor(structure),
         site=as.factor(site),
         data_entry_person=as.factor(data_entry_person),
         month=as.factor(month),
         year=as.factor(year),
         #date=lubridate::as_date(df$date),
         .keep = "unused")
```


## Growth over time: mean area per month


```{r}
# plot con area por araña, no por lado 

df_total <- big |> 
  group_by(date, site, origin, structure_fixed) |> 
  summarise(area_str = sum(area.cm2, na.rm = T)) |> 
  ungroup()

df_plot1 <- df_total |>  
  group_by(date, site) %>% 
  summarise(mean_area = mean(area_str, na.rm = TRUE)) %>% 
  ungroup()

tiff("./Results/Plots/mean_growth.tiff", width = 2000, height = 1200, res = 300)

df_plot1 |> 
  ggplot() +
  geom_line(aes(y=mean_area, x=as.Date(date), color=site))+
  geom_point(aes(y=mean_area, x=as.Date(date), color=site))+
  theme_classic()+
  labs(x = "Date", y = "Mean Area per structure (cm²)") +
  scale_color_manual(values = paleta,
                     labels = c("Güiri-Güiri", "Playa Blanca", "Playa Pelonas")) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "6 months") +
  theme(legend.position = "top",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(angle = 45, hjust = 1)) 

dev.off()
```

## Growth by origin: mean area per month (ending in November 2023)

```{r}
library(RColorBrewer)

df_plot2 <- df_total %>% 
  filter(date <= as.Date("2023-11-30"),
         !is.na(origin)) %>% 
  group_by(date, site, origin) %>% 
  summarise(mean_area = mean(area_str, na.rm = TRUE)) %>% 
  ungroup()

t_palette <- RColorBrewer::brewer.pal(3, "Dark2")

tiff("./Results/Plots/origen.tiff", width = 2000, height = 1200, res = 300)

df_plot2 |> ggplot() +
  geom_line(aes(x = date, y = mean_area, color = origin), linewidth = 1) +
  geom_point(aes(x = date, y = mean_area, color = origin), size = 2) +
  labs(x = "Date", y = "Mean Area per structure (cm²)") +
  theme_classic() +
  scale_color_manual(values = t_palette, 
                     labels = c("Playa Jícaro", "Marina", "Playa Matapalo")) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "6 months") +
  facet_wrap(~site, nrow = 1) +
  theme(legend.position = "top",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(angle = 45, hjust = 1),
        #strip.background = element_rect(fill = "lightgrey"),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5))

dev.off()
```

## Growth over time: mean area per month (small spiders)

```{r}
df <- small %>%
  filter(site=="Playa Blanca") |> 
  group_by(date) %>% 
  summarise(mean_area = mean(area.cm2, na.rm = TRUE)) %>% 
  ungroup()

tiff("./Results/Plots/small_mean.tiff", width = 2000, height = 1200, res = 300)

df |> ggplot() +
  geom_line(aes(x = date, y = mean_area), color = "#192639", linewidth = 1) +
  geom_point(aes(x = date, y = mean_area), color = "#192639", size = 2) +
  labs(x = "Date", y = "Mean Area (cm²)") +
  theme_classic() +
  #scale_color_manual(values = paleta,labels = c("Punta Cacique", "Playa Blanca")) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "6 months") +
  theme(legend.position = "top",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(hjust = 1)) 

dev.off()
```


# Big structures over time.

From here, these are models plots

## Growth Model 1: Playa Blanca, Güiri.

```{r}
tiff("./Results/Plots/overtime.tiff", width = 2000, height = 1200, res = 300)
p3
dev.off()
```

## Growth Model 2: Playa Blanca, Güiri, and Playa Pelonas.

```{r}
tiff("./Results/Plots/overtime3.tiff", width = 2000, height = 1200, res = 300)
p4
dev.off()
```

## Mortality Model 3: Playa Blanca and Güiri.

```{r}
tiff("./Results/Plots/mortality6.tiff", width = 2400, height = 1200, res = 300)
p6
dev.off()
```

## Mortality Model 4: Playa Blanca, Güiri, and Playa Pelonas.

```{r}
tiff("./Results/Plots/mortality4.tiff", width = 2000, height = 1200, res = 300)
p7
dev.off()
```

# Small structures over time.

```{r}

```

## Model 1: Playa Blanca.

```{r}

```

## Model 2: Cacique.

```{r}

```


__________________________________________________________________________________


# Calculate growth rate using the whole data

```{r}
# This calculates the growth rate of the mean area 
# of big spiders per site and date as a percentage change from the previous month.
# percentage of change = (current - previous) / previous * 100
library(gt)

tabla <- df_total %>% 
  group_by(date, site) %>% 
  summarise(mean_area = mean(area_str, na.rm = TRUE)) %>% 
  ungroup() %>% 
  arrange(site, date) |> 
  mutate(growth_rate = (mean_area - lag(mean_area)) / lag(mean_area) * 100) %>% 
  arrange(date) |> 
  pivot_wider(names_from = site, 
              values_from = c(mean_area, growth_rate)) %>%
  select(date, mean_area_Guiri, growth_rate_Guiri, 
         `mean_area_Playa Blanca`, `growth_rate_Playa Blanca`, 
         `mean_area_Playa Pelonas`, `growth_rate_Playa Pelonas`) 

tabla %>% 
  mutate(across(everything(), ~ round(.x, 2))) %>%
  gt()

dim(tabla)
```

```{r}
library(dplyr)
library(lubridate)

# Assuming your data is in a dataframe 'coral_data' with 'date' and 'coral_cover' columns
data <- df_total %>%
  mutate(year = year(date)) %>%  # Extract year from the date
  group_by(year) %>%             # Group by year
  summarise(annual_cover = last(area_str)) # Use the last measurement in each year

# Calculate annual growth rate
data %>%
  arrange(year) %>%
  mutate(growth_rate = (annual_cover - lag(annual_cover)) / lag(annual_cover) * 100) %>%
  filter(!is.na(growth_rate))

```

```{r}
df_total %>%
  mutate(year = year(date)) %>% 
  group_by(year) %>%
  summarise(annual_cover = last(area_str)) %>%
  arrange(year) %>%
  mutate(avg_growth_rate = (annual_cover - lag(annual_cover)) / 1) %>%  # 1 year between measurements
  filter(!is.na(avg_growth_rate))

```


